\section{Creating a guide}\label{sec:Creating_a_guide}
\subsubsection*{Definition} Meaning-carrying tools, like handbooks or maps, can help collect content and stories as well as assist others who want to adopt the idea, .

\subsubsection*{Problem} 
Established ideas have knowledge cartography challenges for newcomers, consider trying to decipher a subway map in a foreign city. When the idea or system is only ``newly discovered'', the associated meanings may not be well understood, and indeed they may not have been created. Even if a topic is only ``personally new'', it can be hard to find one's way around.

\subsubsection*{Solution}
The process of creating the guide can go hand-in-hand with figuring out how the system works. Thus, techniques of \href{http://knowledgecartography.org/}{knowledge cartography} and \href{http://www.hitl.washington.edu/publications/r-97-47/two.html}{meaning making} are useful for would-be guide creators.\footnote{We started the Peeragogy project by collaboratively making an outline for the Peeragogy Handbook. We recommended this
handbook-making practice to others, as a way to learn collaboratively and build a strong group.}

\subsubsection*{Challenges} 
It is important to keep in mind how ``the map is not the territory,'' and map-making is only one facet of shared human activity. For instance, a pattern description can be thought of as a ``micro-map'' of a specific activity. These maps are not useful if they are divorced from practice.

\subsubsection*{What's Next} 
Working with our shepherd at PLoP to improve this paper!


