\section{Peeragogy}\label{sec:Peeragogy} 
%% Possibly change to Peeragogy in Action.
%% Maybe change Wrapper to Wrap Up, or call the other patterns according to roles
% DK: I question whether the Peeragogy Project is a pattern, or an instance of a pattern. We generally think about patterns as something that can be instantiated. But your project seems like a specific case of the concept.
% JC: There could be many projects

\subsubsection*{Motivation} This pattern provides an entry point to the other patterns.  It is relevant to anyone who wants to do active learning together with others in a relatively non-hierarchical setting.

\subsubsection*{Context}  Architectual maverick Christopher Alexander asked the following questions to an audience of computer programmers \cite{alexander1999origins}: 
\begin{quote}
``What is the Chartres of programming? What task is at a high enough level to inspire people writing programs, to reach for the stars?''
\end{quote}
In order for humanity to pull itself up by its bootstraps, on this planet or any other, we need to continue to learn and adapt.  Collaborative projects like Wikipedia, StackExchange, and FLOSS represent an implicit challenge to the old ``industrial'' organization of work.  This new way of working appears to promise something more resilient, more exciting, and more humane.  In the context of these free, open, post-modern organizations, individual participants are learning and growing -- and adapting the methods and infrastructure as they go.
Because everyone in these projects primarily learns by putting in effort on a shared work-in-progress, participants are more in touch with an \emph{equality of intelligence} than an \emph{inequality of knowledge} \cite[pp.~38,119]{ranciere1991ignorant}.
At the same time, they invoke a form of friendly competition, in which \emph{the best craftmanship wins} \cite[p.~89]{raymond2001cathedral}.
%%% FORCES

\subsubsection*{Forces}

\raisebox{-.5\baselineskip}
{{\centering
\begin{tabular}{p{.85\textwidth}}
\textbf{Threshold}: there is a tension between inclusiveness and specificity.\\
\textbf{Trust}: is only built through sharing and reciprocity.
\end{tabular}

\par}}

\subsubsection*{Problem} Even a highly successful project like Wikipedia is a work in progress that can be improved to \emph{\emph{better} empower and engage people around the world, to develop \emph{richer and more useful} educational content, and to disseminate it \emph{more} effectively} -- and deploy it more creatively.\footnote{\url{https://wikimediafoundation.org/wiki/Mission_statement}}  How to go about this is a difficult question, and we don't know the answers in advance.  There are rigorous challenges facing smaller projects as well, and fewer resources to draw on.  Many successful free software projects are not particularly collaborative -- and the largest projects are edited only by a small minority of users \cite{free-software-better,who-writes-wikipedia}.  Can we work smarter together?

\subsubsection*{Solution} People who learn actively together talk to each other about material problems, share practical solutions, and constructively critique works-in-progress.  There are many different ways to go about this -- bug reports, mailing lists, writers workshops, Q\&A forums, watercoolers and skateparks are all places where peeragogy can happen.  In the Peeragogy project have found that the necessary ``reflection'' aspects of the process are particularly well-matched to Christopher Alexander's idea of a \emph{pattern language}, in which commonly occurring,  interconnected, elements of an optative design are refined until they can be described in terms of a simple template.  Indeed, thought of as a design pattern, \patternname{Peeragogy} can be understood as an up-to-date revision of Alexander's \patternnameext{Network of Learning} \cite[p. 99]{alexander1977pattern}.  It \emph{decentralizes the process of learning and enriches it through contact with many places and people} -- in interconnected networks that may reach all over the world.   Importantly, while people involved in a peeragogical process may be collaborating on \patternname{A specific project}, they don't have to be direct collaborators outside of the learning context or co-located in time or space.  Peeragogy often takes place in mostly-horizontal relationships between people who have different but compatible objectives.  The techniques we describe with these patterns are in many cases ancient; one can compare, for instance, the Quechua communal working practice of \emph{mink'a}.  The underlying practices can be pursued with or without high technology and with or without the technique of design patterns.  
% Can we clarify that we're describing Peeragogy as a pattern, and a pattern language, and that it is useful whether or not others decide to use patterns...
%OSS: We talk about patterns - does this mean learners are meant to organize their knowledge in new patterns? Would be great if learners made new patters, but we're not requiring that and we need to be more explicit about that? May also be useful for people into pattersns


\subsubsection*{Rationale}
% DK: I have written many, and shepherded many more, and I don’t think this is the case. However, the effort that goes into writing them makes them more intuitive to read :+)
The peeragogical approach particularly addresses the problems of small projects stuck in their individual silos, and large projects becoming overwhelmed by their own complexity.  It does this by going the opposite route: explicating \emph{what by definition is tacit} and employing \emph{a continuous design process} \cite[pp. 9--10]{schummer2014beyond}.  The very act of asking ``can we work smarter together?'' puts learning front and center.  \patternname{Peeragogy} takes that ``center'' and distributes it across a pool of heterogeneous relationships.  As pedagogy articulates the transmission of knowledge from teachers to students, peeragogy articulates the way peers produce and use knowledge together (Figure \ref{fig:connections}).  Active learning together with others brings social and emotional intelligence to bear on the things that matter most.

\subsubsection*{Resolution}

Peeragogy helps people in different projects describe and solve real problems. 
If you share the problems that you're experiencing in your project, someone may be able to help you solve them.  Bringing a problem across the \textbf{threshold} of someone else's awareness helps achieve clarity.  
This process can guide individual action in ways that we wouldn't have seen on our own, and may lead to new forms of collective action we would never have imagined possible.  People who gain experience comprehending problems together build \textbf{trust}.
%
Making room for multiple right answers helps to resolve the tension between generality and specificity.
The Peeragogy project is one of ``tens of thousands of projects in the traditions of world improvement \'elan -- without any central committee that would have to, or even could, tell the active what their next operations should be'' \cite[p. 402]{sloterdijk2013change}.  When we talk about ``next steps,'' we aim to clarify our own commitments, and show what can be realistically expected from us.

\subsubsection*{Example 1} Wikipedia and its sister sites rely on user generated content,
peer produced software, and are managed, by and large, by a pool of users who choose to
get involved with governance and other ``meta'' duties.
%
Wikimedia's pluralistic approach achieves something quite impressive: the
Wikimedia Foundation runs the 7\textsuperscript{th} most popular
website in the world, and has under 300 employees.  For comparison,
the 6\textsuperscript{th} (Amazon) and 8\textsuperscript{th} (QQ) most popular
websites are run by companies with over 200K and 28K employees,
respectively.\footnote{\url{https://en.wikipedia.org/wiki/Wikimedia_Foundation\#Employees}}\textsuperscript{,}\footnote{\url{http://phx.corporate-ir.net/phoenix.zhtml?c=97664&p=irol-newsArticle&ID=2100418}}\textsuperscript{,}\footnote{\url{https://www.google.com/finance?cid=695431}}\textsuperscript{,}\footnote{\url{http://www.alexa.com/topsites}}
%OSS: which ones are they?   

\subsubsection*{Example 2} Although one of the strengths of \patternname{Peeragogy} is to
distribute the workload, this does not mean that infrastructure is
irrelevant.  No less than their predecessors, the students and
researchers of the future university will need access to an
Observatory and other scientific apparatus if they are truly to reach \emph{ad astra, per aspera}.\footnote{``With difficulty, to the stars.''}

\begin{framed}
\noindent 
\emph{What's next.}
\definecollection{PeeragogyWN}
\begin{collectinmacro}{\PeeragogyWN}{}{}
We intend to revise and extend the patterns and methods of peeragogy to make it a workable model for learning, inside or outside of institutions.
\end{collectinmacro}
\PeeragogyWN
\end{framed}

% People won't get invested without a return, although this may not be the same for everyone.
% , and the idea of a specific goal or something concrete on offer


  

  
  
  
  
  
  
  
