% arara: pdflatex
% arara: bibtex
% arara: pdflatex
% arara: pdflatex
\documentclass{llncs}

\usepackage{fontspec}                                          
\setmainfont[Ligatures=TeX,
               SmallCapsFont={Latin Modern Roman Caps}
              ]{Latin Modern Roman} 

\newcommand{\icon}{\fontspec{Symbola}}

\usepackage{placeins}
\usepackage[numbers]{natbib}

\let\oldcite\cite
\let\cite\citep
\let\citeA\oldcite
\let\citeNP\oldcite
\let\citeyear\citeyearpar

\usepackage[table,dvipsnames]{xcolor}

\usepackage{tabularx}

%\usepackage{colortbl}

\usepackage{framed}

\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{positioning,backgrounds,fit,arrows,arrows.meta,shapes,shadows}
\usetikzlibrary{shapes.multipart}
%\usepackage{pgflibraryarrows}

\usepackage{wrapfig}


\usepackage{latexsym}
\usepackage{amsfonts,amsmath,amssymb}
\usepackage{url}
\usepackage[utf8]{inputenc}
\PassOptionsToPackage{hyphens}{url}
\usepackage{hyperref}
\makeatletter
\g@addto@macro{\UrlBreaks}{\UrlOrds}
\makeatother
%\usepackage[hyphenbreaks]{breakurl}
%\usepackage[hyphens]{url}
\hypersetup{colorlinks=false,pdfborder={0 0 0}}
%\usepackage{textcomp}
%\usepackage{longtable}
\usepackage{multirow,booktabs}

\newcommand{\patternname}[1]{\hyperref[sec:#1]{{\sc #1}}}
\newcommand{\patternnameext}[1]{{\sc #1}}
\newcommand{\patternnameplural}[1]{\hyperref[sec:#1]{{\sc #1s}}}
\newcommand{\patternnameposesssive}[1]{\hyperref[sec:#1]{{\sc #1's}}}

\usepackage{collect}

%% \makeatletter
%% \newcommand{\store}[2]{\definecollection{#1}
%% \begin{collectinmacro}{\@nameuse{#1}}{}{}
%% #2
%% \end{collectinmacro}%
%% \@nameuse{#1}
%% \makeatother

% test commit from Papeeria

\title{Patterns of Peeragogy}
\author{Joseph Corneli \and
Charles Jeffrey Danoff \and
Charlotte Pierce \and 
Paola Ricaurte \and 
Lisa Snow Macdonald}

\institute{Department of Computing, Goldsmiths College, University of London \\
\url{j.corneli@gold.ac.uk}\\[.5mm]
Mr Danoff's Teaching Laboratory \\
\url{danoff.charles@gmail.com}\\[.5mm]
Pierce Press and Independent Publishers of New England \\
\url{charlotte.pierce@gmail.com}\\[.5mm]
Department of Cultural Studies, Tecnol\'ogico de Monterrey \\
\url{ricaurte.paola@gmail.com}\\[.5mm]
independent researcher and consultant, Los Angeles\\
\url{snowinla@yahoo.com}
}

\begin{document}

\maketitle

\begin{abstract}
We describe nine design patterns that we have developed in our work on the Peeragogy project, in which we aim to help design the future of learning, inside and outside of institutions.  We use these patterns to build an ``emergent roadmap'' for the project.

\keywords{peer production, peer learning, design patterns}
\end{abstract}

\input{Introduction}        % \label{sec:Introduction}
\input{Peeragogy_Project}   % \label{sec:Peeragogy}
\input{Roadmap}             % \label{sec:Roadmap}
\input{Use_or_make}         % \label{sec:Reduce, reuse, recycle}
\input{Carrying_capacity}   % \label{sec:Carrying capacity}
\input{A_specific_project}  % \label{sec:A specific project}
\input{Wrapper}             % \label{sec:Wrapper}
\input{Heartbeat}           % \label{sec:Heartbeat}
\input{Newcomer}            % \label{sec:Newcomer}
\input{Scrapbook}           % \label{sec:Scrapbook}
\input{Distributed_Roadmap} % \label{sec:Distributed_Roadmap}
\input{Conclusion}

\bigskip

%% {\fontsize{10}{12}\selectfont\raggedright\uppercase{Acknowledgements}} \label{sec:Acknowledgements}\newline
%% \vspace{-.2cm}
%% \noindent

\subsection*{Acknowledgements}
David Kane was the paper's shepherd for PLoP'15, and provided detailed
comments and many suggestions that improved the draft.  Philip Bachman
was our on-site shepherd, and Mary Lynn Manns was our workshop
facilitator.  The paper also benefited from discussions with Doug
Breitbart, Marian Petre, and the late George Brett, as well as
feedback from writers' workshop participants.  We are grateful to
Amanda Lyons and Fabrizio Terzi for their contributed images.  Photographs
and icons were sourced from the public domain.

Joseph Corneli was supported by the Future and Emerging Technologies
(FET) programme within the Seventh Framework Programme for Research of
the European Commission, under FET-Open Grant number 611553
(COINVENT).

%\newpage
\bibliographystyle{splncsnat}
\bibliography{peeragogy-bib}


\end{document}
