\begingroup \color{BurntOrange}

\section{Don't make what you can simply use, and don't sell what you can afford to give away} \label{sec:Use_or_make}

\subsubsection*{Context}
Peer production, as the name indicates, is about producing, in other words -- ``making stuff.'' But we do this by building on the work of others.  Similarly, learning something new generally involves connecting deeply with what's already there.  The idea of being innovative is celebrated in our culture.  In academia, it's all about ``impact,'' and in business, it's all about the bottom line.  These things don't come from nowhere. 

\subsubsection*{Problem}
People are often very attached to their own projects and priorities and don't have a sense of how their initiatives can benefit from connecting with others. Many projects die because the cost of \patternname{\href{http://c2.com/cgi/wiki?ReinventingTheWheel}{Reinventing the Wheel}} [c2] is too high.  We're often blind to the obstacles that we put in our own path.

\subsubsection*{Solution} Learning and creativity often involve recycling and remixing others' ideas and techniques.   Duchamp's {\href{https://en.wikipedia.org/w/index.php?title=Readymades_of_Marcel_Duchamp&oldid=660437742}{readymades}} were a reaction against a narrow perspective on originality.  Contemporary DJs turn songs that already exist into new modes of musical expression.  While it's a great idea to ``steal like an artist'' don't forget to return the favor and make it possible for other people to remix and adapt your work too.  One good start is to give it away, then it's not technically stealing when others use it \cite{anderson2009free}. In our case, we've released the \emph{Peeragogy Handbook} using the Creative Commons Public Domain Dedication (CC0), a legal instrument grants the greatest possible leeway to downstream users.\footnote{\url{https://creativecommons.org/publicdomain/zero/1.0/}}  Show appreciation when someone takes up the offer.  (In the case of shared content, make backups so that you don't have to worry about losing the record of idea that another person might not have noticed was important.)

\subsubsection*{Rationale} 
\patternname{Creating a guide} can help people avoid reinventing the wheel. Clearly we are not the first people to notice these things!  Consider the following quote from the Wikimedia Foundation: ``Unfortunately, many of our most valuable resources for learning and evaluation are scattered across wikis, buried in archived reports, incomplete, out of date, or are only available in a single language. As a result, we sometimes find ourselves re-inventing the wheel: missing opportunities, repeating common mistakes, and working harder than we need to because we are not aware of related projects done by others who came before us.'' via \url{https://blog.wikimedia.org/2013/11/19/learning-patterns-new-way-share-important-lessons/}.  There are lots of tools and approaches out there -- \emph{use them}, at least on a trial basis; return to the ones that work.\footnote{As Willow Brugh of Geeks without Bounds and the MIT Media Lab remarked as a guest in one of our hangouts (\url{https://www.youtube.com/watch?v=NpyQfYVKfBI}): people often think that they need to build a community, and so fail to recognize that they are already part of a community.}

\subsubsection*{Resolution} Noticing how difficult it is to remake things every time, and encapsulating what we observed with the \patternname{Use or Make} pattern reminds us to always consider re-purposing the work of others, to think about how others can leapfrog ahead, building on our experiences by incorporating our work.

\subsubsection*{What's Next} We've spun off the pattern catalog from the \emph{Peeragogy Handbook} into this paper, sharing it with a new community and gaining new perspectives.  Let's look for other parts of the handbook we can spin off!

\endgroup
    
    
    
    